Import and process AODV3 Level2 AOD20 from Aeronet

### 2019-08-05 Code/03_import_AOD_V3.Rmd
within day variation plot

Borrowed some code from `03_import_aeronet.R` on Jdrive  
Import and process the AOD20 V3 level 2 global Aeronet stations  
Interpolating to wavelength AOD 470nm

```{r, eval = F, include = F}
## About this script ##

```{r}
source("~/liuyanguu/CWV/Code/cwv_funcs.R")
source(here::here("Code", "funcs_for_plots.R"))

>>>>

Borrowed some code from `03_import_aeronet.R` on Jdrive  
Import and process the AOD20 V3 level 2 global Aeronet stations  
* Interpolating to wavelength AOD 470nm, the result is: 
`aod20_data_pred470 <- read.fst("/data-coco/ECHO_PM/AeronetAODV3Level2/AOD_Level20_All_Points_V3_wPredAOD_470nm_190618.fst", as.data.table = T)`

* Collocate with MCD19A2

```{r}
source("~/liuyanguu/CWV/Code/cwv_funcs.R")
source("~/liuyanguu/AOD_CONUS/Code/funcs_for_plots.R")
